### 2014-12-04 tex/short_2015/body.tex
mainly figures

@@

\begin{figure}[htb]
  \centering
  \subfigure[Server-rendered]{
    \includegraphics[width=.3\linewidth]{splat1.jpg}
  }
  \subfigure[$P_c M_c = P_s M_s$]{
    \includegraphics[width=.3\linewidth]{splat1.jpg}
  }
  \subfigure[$P_c M_c \neq P_s M_s$]{
    \includegraphics[width=.3\linewidth]{splat2.jpg}
  }
  \caption{\label{fig:LargeSplatsOnCorners}
           Splats for which depths are sampled on a planar region look nice on
  exactly this region, but contorted elsewhere, notice the corner of the cube.}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \subfigure[Low quality (tenker her jpg med q=0 og daarlig dybdebuffer, faa
  splats kanskje]{
    \input{fig3a.tex}
  }
  \subfigure[High quality (png med maks av alt, mange splats)]{
    \input{fig3b.tex}
  }
  \caption{\label{fig:adapativeProxyModels}
           Proxy models adaptively adjusted to available bandwidth and server
           capacity.}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \subfigure[Server-rendered]{
    \input{fig3a.tex}
  }
  \subfigure[Client-rendered proxy model]{
    \input{fig3b.tex}
  }
  \caption{\label{fig:FRView}
           The oil reservoir viewer FRView}
\end{figure}

>>>>

\item problem med shading/shadows ++ i forb. med ikke deferred shading/normal map

\item About our test case: corners, smooth surfaces, texturing for which artifacts are easy to
spot. What it does lack is self-occluding parts. The FRView rservoir model that
we have tested on does contain some of this.

\item Burde vi vise chemco?

@@

\begin{figure}[htb]
  \centering
  \subfigure[Server-rendered]{
    \includegraphics[width=.3\linewidth]{splat1.jpg}
  }
  \subfigure[$P_c M_c = P_s M_s$]{
    \includegraphics[width=.3\linewidth]{splat2.jpg}
  }
  \subfigure[$P_c M_c \neq P_s M_s$]{
    \includegraphics[width=.3\linewidth]{splat3.jpg}
  }
  \caption{\label{fig:LargeSplatsOnCorners}
           Splats for which depths are sampled on a planar region look nice on
  exactly this region, but contorted elsewhere, notice the corner of the cube.}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \subfigure[Full png]{
    \includegraphics[width=.30\linewidth]{auto1.jpg}
  }
  \subfigure[Coarse jpg]{
    \includegraphics[width=.30\linewidth]{auto2.jpg}
  }
  \subfigure[Auto-proxy w/$260^2$ splats and 1/256 rgb to depth fragment ratio]{
    \includegraphics[width=.30\linewidth]{auto3.jpg}
  }
  \caption{\label{fig:adapativeProxyModels}
           Proxy models adaptively adjusted to available bandwidth and server
           capacity. The server-rendered JPG image adaptively selects a quality
  setting based on timing of image sending. Shown is the worst
  case, \texttt{quality}=0, which is the last step before switching to ``auto
  proxy''. The auto-proxy shown displays artifacts caused by the magenta surface
  to being almost parallel to the viewing direction at the moment of proxy model
  recording, the number of splats is set low ($260^2$) on purpose, and the depth
  buffer size is reduced by a factor of $16^{-2} \approx 0.4\%$.}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \subfigure[Server-rendered]{
    \includegraphics[width=.47\linewidth]{frview1.jpg}
  }
  \subfigure[Client-rendered proxy model]{
    \includegraphics[width=.47\linewidth]{frview2.jpg}
  }
  \caption{\label{fig:FRView}
           The oil reservoir viewer FRView. Not that we have chosen parameters
  (small number of splats ($128^2$), forcing display of splats that would normally be
  discarded) to emphasize artifacts, \eg, the ragged edges, a few holes, and the
  oddly placed (and rendered) axis indicator.}
\end{figure}
